A Comparative Quality Metric for Untargeted Fuzzing with Logic State Coverage

### 2024-06-06 paper/main.tex
checkpt

\autoref{f:repr} shows an example control-flow graph and its logic space,
gridded up by the different hit counts $m(b)$ of the branch $b_1$, $b_2$, and $b_3$.
%, where $m(b)$ denotes the hit count of a branch $b$. 
Each colored box represents one logic state that includes all program
behaviors that exhibit the branch hit counts at the enclosed grid points.
For example, a program behavior that does not hit any of $b_1$, $b_2$, and $b_3$ 
(i.e., $m(b_1)=m(b_2)=m(b_3)=0$) falls into the \cbox{black} logic state, while
all program behaviors that hit only $b_1$ (i.e., $m(b_1)>1$ and
$m(b_2)=m(b_3)=0$) fall into the \cbox{red} logic state.
%, and all program behaviors that hit only $b_2$ and $b_3$ (i.e.,
%$m(b_1)>1$, $m(b_2)>1$, and $m(b_3)=0$) fall into the \cbox{cyan} logic state.

The colored boxes in \autoref{f:repr} suggest the increasing size of logic
states as their constituent program behaviors involve more repetitive branches.
To be specific, a logic state covers a progressively larger volume 
%in the logic space 
(i.e., \cbox{black} $\rightarrow$ \cbox{red}/\cbox{green}/\cbox{blue}
$\rightarrow$ \cbox{yellow}/\cbox{cyan}/\cbox{magenta} $\rightarrow$
\cbox{gray}) as it contains more repetitive branches (i.e., 0 $\rightarrow$ 1
$\rightarrow$ 2 $\rightarrow$ 3 repetitive branches). 
%
This results in repetitive (i.e., uninteresting) program states packed
to fewer logic states, suppressing (boosting) logic state coverage as it observes more
uninteresting (interesting) behaviors.
%\footnote{It is worth noting that a coordinate in the grid does
%\emph{not} represent one program behavior. For example, a coordinate (1, 1, 0)
%represents two program behaviors, $b_1$ before $b_2$ and $b_2$ before $b_1$.
%However, it does not affect the relative size of visualized logic states because
%a coordinate only has more program behaviors as it gets further from the
%origin.}

>>>>

\autoref{f:repr} shows an example control-flow graph and its logic space,
gridded up by the different hit counts $m(b)$ of the branch $b_1$, $b_2$, and $b_3$.
%, where $m(b)$ denotes the hit count of a branch $b$. 
Each colored box represents one logic state, which includes all program
behaviors that fall into the box.
For example, a program behavior that does not hit any of $b_1$, $b_2$, and $b_3$ 
(i.e., $m(b_1)=m(b_2)=m(b_3)=0$) belongs to the \cbox{black} logic state, while
all program behaviors that hit only $b_1$ (i.e., $m(b_1)>1$ and
$m(b_2)=m(b_3)=0$) fall into \cbox{red}.
%, and all program behaviors that hit only $b_2$ and $b_3$ (i.e.,
%$m(b_1)>1$, $m(b_2)>1$, and $m(b_3)=0$) fall into the \cbox{cyan} logic state.

The colored boxes in \autoref{f:repr} suggest the increasing size of logic
states as their constituent program behaviors involve more repetitive branches.
To be specific, a logic state covers a progressively larger volume 
in the logic space 
(i.e., \cbox{black} $\rightarrow$ \cbox{red}/\cbox{green}/\cbox{blue}
$\rightarrow$ \cbox{yellow}/\cbox{cyan}/\cbox{magenta} $\rightarrow$
\cbox{gray}) as it contains more repetitive branches (i.e., 0 $\rightarrow$ 1
$\rightarrow$ 2 $\rightarrow$ 3 repetitive branches). 
%
This results in repetitive (i.e., uninteresting) program states packed
to fewer logic states, suppressing (boosting) logic state coverage as it observes more
uninteresting (interesting) behaviors.
%\footnote{It is worth noting that a coordinate in the grid does
%\emph{not} represent one program behavior. For example, a coordinate (1, 1, 0)
%represents two program behaviors, $b_1$ before $b_2$ and $b_2$ before $b_1$.
%However, it does not affect the relative size of visualized logic states because
%a coordinate only has more program behaviors as it gets further from the
%origin.}
